Ten Years of TTC Delays an Analysis

### 2024-09-27 outputs/paper/paper.qmd
fix refs

---
title: "Ten Years of TTC Delays an Analysis"
author: Robert Ford
thanks: "Code and data are available at: https://github.com/Ford-Robert/STA304_City-Of-Toronto-Data.git"
date: 27/09/2024
date-format: 27 September 2024
abstract: "This study analyzes ten years of delay data from the Toronto Transit Commission (TTC), focusing on subways, streetcars, and buses to assess changes in delay times of these services. The analysis found that buses experience the highest number of delays and the longest total and average delay times, while subway delays are resolved much faster on average. The analysis also delves into the specific challenges each service faces, analyzing which incidents they are most likely to experience and how long those incidents take to resolve. These findings provide data-driven insights for improving TTC operations and uncovering the specific challenges faced by each transportation mode."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

>>>>

---
title: "Ten Years of TTC Delays an Analysis"
author: Robert Ford
thanks: "Code and data are available at: https://github.com/Ford-Robert/STA304_City-Of-Toronto-Data.git"
date: 27/09/2024
date-format: 27 Sept 2024
abstract: "This study analyzes ten years of delay data from the Toronto Transit Commission (TTC), focusing on subways, streetcars, and buses to assess changes in delay times of these services. The analysis found that buses experience the highest number of delays and the longest total and average delay times, while subway delays are resolved much faster on average. The analysis also delves into the specific challenges each service faces, analyzing which incidents they are most likely to experience and how long those incidents take to resolve. These findings provide data-driven insights for improving TTC operations and uncovering the specific challenges faced by each transportation mode."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

All data was collected and cleaned using R (@citeR), and its tidyverse (@citetidyverse), lubridate (@lubridate), and readxl (@citereadxl) packages.
